---
title: "Article Quality Assessment"
output: html_document
---

```{r, settings, echo=FALSE}
knitr::opts_chunk$set(cache=FALSE, warning=FALSE,
    message=FALSE, fig.align='center', fig.width=10)
```

```{r, load_library}
library(RSQLite)
library(dplyr)
library(ggplot2)
library(stringr)

checkDuplicate = function(rawArticle, dataSource){
    sub = 
        rawArticle %>%
        subset(., source == dataSource)

    duplicateCount =
        sub %>%
        group_by(title) %>%
        summarise(count = n()) %>%
        arrange(., desc(count))
    
    cat("Data source: ", dataSource, "\n")
    cat("Total number of entry: ", NROW(sub), "\n")
    cat("Unique Titles: ", length(unique(sub$title)), "\n")
    cat("Most duplicated title is: '", unlist(duplicateCount[1, "title"]), "'\n", sep = "")
    cat("Duplicate count summary:\n")
    print(summary(duplicateCount$count))
    cat("\n")
}

getDuplicated = function(rawArticle, dataSource, n = 1){

    sub = 
        rawArticle %>%
        subset(., source == dataSource)

    duplicateCount =
        sub %>%
        group_by(title) %>%
        summarise(count = n()) %>%
        arrange(., desc(count))

    
    sub %>%
        subset(., title == unlist(duplicateCount[n, "title"]))
}

```


```{r, load_data}
dataDir = Sys.getenv("DATA_DIR")
dbName = "/the_reading_machine.db"
fullDbPath = paste0(dataDir, dbName)
con = dbConnect(drv=SQLite(), dbname=fullDbPath)
statement = paste0('SELECT * FROM RawArticle')
rawArticles =
    dbGetQuery(con, statement) %>%
    mutate(date = as.Date(date, format="%Y-%m-%d  %H:%M:%S"))
```

There are a few observations we can make in the following graph. First
of all, we can see that the Bloomberg data does not start until the
end of 2011. Further, the number of articles remain low prior to early
2012. This is an indication of a problem with the scraper unable to
trace back to articles prior to 2011. This
[article](https://www.bloomberg.com/news/articles/2004-04-18/separating-the-wheat-from-the-chaff)
is from 2004 and has the exact same link structure as one in recent
year was not scrapped. Further investigation is required and
improvements to the scraper is required.

Secondly, We can see that the number of articles from World Grain is
relatively higher but the frequency of publication is significantly
lower. 

```{r, aggregated_article_count}
aggregatedCount =
    rawArticles %>%
    group_by(date, source) %>%
    summarise(count = n())

ggplot(data = aggregatedCount, aes(x = date, y = count)) +
    geom_line() +
    facet_wrap(~source)
```

If we look on the log scale, the number of Bloomberg article also
increased considerably in 2016 which also happened to be the latest
year. In contrast, both Euractive and Agrimoney increase either
steadily or remained constant. This suggests there may be some issues
in going back in time for Bloomberg articles.

```{r}
ggplot(data = aggregatedCount, aes(x = date, y = count)) +
    geom_line() +
    facet_wrap(~source) +
    scale_y_log10() +
    geom_smooth()
```



A quick inspection of the World Grain data reveals that all the
articles occur on the first day of the month. After inspecting the
scraper, it is apparent that the date were parsed according to the
link of article. However, the link contains only year and month
information. Thus, we will need to parse the date differently for
World Grain.

```{r}
aggregatedCount %>%
    subset(., source == "worldgrain") %>%
    data.frame
```

## Duplicates

One of the issues identified earlier in the project was the
duplication of the articles. Below is a small summary of the
duplication for each data source.

```{r}
for(i in unique(rawArticles$source)){
    checkDuplicate(rawArticles, i)
}
```

The reason for each source differs and require different solution for
each problem.

### Bloomberg

Although Bloomberg has a low level of duplication, it seems that the
title or the link is extracted incorrectly in certain cases.

Take the following example, the title for all the articles below are
'Bloomberg' which is evidently incorrect.

```{r}
rawArticles %>%
    getDuplicated(rawArticle = ., dataSource = "bloomberg", n = 1) %>%
    select(., c(link, title))
```


This second example also shows the same problem where the title is
duplicated and on of them is incorrect. Further, the `http` and
`https` address are treated differently where they should be the same.

```{r}
rawArticles %>%
    getDuplicated(rawArticle = ., dataSource = "bloomberg", n = 2) %>%
    select(., c(link, title))
```


### Agrimoney

Similar to Bloomberg, the number of duplicated article is also
low. The most 2 common problem with Agrimoney is that maintenance and
service page are being scrapped.

The most common problem is the reduced service information page.

```{r}
rawArticles %>%
    getDuplicated(rawArticle = ., dataSource = "agrimoney", n = 1) %>%
    select(., c(link, title))
```

Followed by maintenance information page.

```{r}
rawArticles %>%
    getDuplicated(rawArticle = ., dataSource = "agrimoney", n = 2) %>%
    select(., c(link, title))
```

These entries should be eliminated or ignored. Links ending with
`reduced-service-at-agrimoney.com` or
`apology-to-agrimoney.com-subscribers` should be skipped.


In addition, same article can be featured in different section as
demonstrated in the following example.

```{r}
rawArticles %>%
    getDuplicated(rawArticle = ., dataSource = "agrimoney", n = 4) %>%
    select(., c(link, title))
```

We also need to account for this when scrapping from Agrimoney.


### Euractive

In contrast to the low level of duplicate of Bloomberg and Agrimoney,
Euractive has more than 50% of articles duplciated. 

First of all, entry with the title `News – EurActiv.com` are not
actual entries and analysis of the scrapper should be conducted to
identify why these links are extracted.

```{r}
rawArticles %>%
    getDuplicated(rawArticle = ., dataSource = "euractiv", n = 1) %>%
    select(., c(link, title))
```

The second type of problem is also identified above with no
distinction between the `http` and `https` version of the
website. Further, there seem to be odd suffix at the end of the link
which refers to the same article.

```{r}
rawArticles %>%
    getDuplicated(rawArticle = ., dataSource = "euractiv", n = 2) %>%
    select(., c(link, title))
```

Finally, again, we need to account for news articles appearing in
different section.

```{r}
rawArticles %>%
    getDuplicated(rawArticle = ., dataSource = "euractiv", n = 3) %>%
    select(., c(link, title))
```



### World Grain

Finally, we investigate the World Grain data. Despite the huge number
of duplication, the source came mainly from two issues.

First, the website supports mobile viewing. Thus, they were also
scrapped and indistinguished like the `http/s` problem. Further, World
Grain has articles spanning multiple page which has multiple
links. Thus, entries although refer to parts of the article are
treated separate entries by the scrapper.

The question regarding the multi-page issue depends on the type of
model we will be dealing with and can be either left alone or require
merging of the articles.

```
rawArticles %>%
    getDuplicated(rawArticle = ., dataSource = "worldgrain", n = 1) %>%
    select(., c(link, title))
```

Nonetheless, the issue of duplication is a minor one as
post-processing can help eliminate all the issues identified.


## Length of Articles

Below we show the length of the article for each soruce. It seems that
Bloomber and Euroactiv has some text that is extremely long.

```{r}
wordCount = 
    rawArticles %>%
    mutate(wordCount = str_count(article, "[[:alpha:]]+"))


wordCount %>%
    ggplot(data = ., aes(factor(source), wordCount)) +
    geom_violin()
```


A investigation reveals that the longest article is actually not an
article, rather a live feed. The long articles from Bloomberg are
meeting minutes and transcripts. This might be a piece of information
that might be useful in the modelling.

```{r}
wordCount %>%
    arrange(., desc(wordCount)) %>%
    select(., title) %>%
    unique %>%
    head(., 10)
```

## Productionise

In order for the scraper to be properly integrated and sustainable,
there are several changes to that needs to be put in place.

First of all, we need to research on a method to only search for
recent text on text that has not been extracted. The scraper currently
takes a few hours to execute and the duration will continue to
increase over time. Thus, it is desirable to reduce the run time and
redudancy of the scraper.


Currently the data is saved as a `jsonl` file. We should load this
into a database directly for future use.



## List of TODOs

P0:

* Parse the data differently for World Grain

P1:

* Investigate the Bloomberg scraper and identify the problem
* Scrap data for Bloomberg prior to 2012.
* Upon finishing the updates, integrate the scraper into the pipeline.

P3:

* Treat `http` and `https` equally.
* Remove the maintenance and service page of Agrimoney
* Skip same article from different news section.
* Account for mobile version of the website.
